---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# private

* Functions that are defined in the body of other functions cannot be tested easily
and clutter the body of the parent function, it's also not always clear if they use
lexical scoping or not
* If we move these functions to the namespace they make the codebase harder to
understand because we lose this relationship

{private} proposes a solution to these problems.


## Installation

Install with:

``` r
remotes::install_github("moodymudskipper/private")
```

## Example


```{r example}
library(private)
print_cubed <- function(x) {
  x |> cube() |> format()
}
print_cubed %private% cube <- function(x) {x * square(x)}
# this works recursively
print_cubed %private% cube %private% square <- function(x) {x^2}
print_cubed %private% format <- function(x) {paste("Square value:", x)}

print_cubed(3)

# parents have a printing method
print_cubed

# children too
print_cubed %private% format

# they work together
print_cubed %private% cube

# private closures are not bound to the local environment (the namespace if we're in a package)
ls()

# we can test the private methods
(print_cubed %private% cube)(4)
```

